fdcoexist

### 2018-08-23 paper_simulations.Rmd
:sparkles: Explicit carrying capacity
Co-authored-by: Rekyt <matthias.grenie@ens-lyon.fr>
Co-authored-by: pierredenelle <pierre.denelle@cefe.cnrs.fr>

n_patches  <- 25   # Number of patches
n_species  <- 100  # Number of species
n_gen      <- 150  # Length of model run (generations)
initpop    <- 50   # initial population size
n_traits   <- 3    # number of traits
k          <- 1.15 # Maximum growth rate
env_width  <- seq(10, 10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength

@@

```{r simul_no_compet_no_corr}
no_compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = env_width)
    })

@@

```{r simul_no_compet_low_cor}
no_compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = env_width)
    })

@@

```{r simul_no_compet_high_cor}
no_compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = env_width)
    })

@@

```{r simul_compet_no_corr}
compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = env_width)
    })

@@

```{r simul_compet_low_corr}
compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = env_width)
    })

@@

```{r simul_compet_high_corr}
compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = env_width)
    })

@@

no_compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

@@

```{r simul_no_compet_low_cor var_strength}
no_compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

@@

```{r simul_no_compet_high_cor var_strength}
no_compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width)
    })

@@

```{r simul_compet_no_corr var_strength}
compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

@@

```{r simul_compet_low_corr var_strength}
compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

@@

```{r simul_compet_high_corr var_strength}
compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width)
    })

>>>>

n_patches <- 25   # Number of patches
n_species <- 100  # Number of species
n_gen     <- 150  # Length of model run (generations)
initpop   <- 50   # initial population size
n_traits  <- 3    # number of traits
k         <- 1.15 # Maximum growth rate
K         <- 150  # Carrying capacity
env_width <- seq(10, 10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength

@@

```{r simul_no_compet_no_corr}
no_compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

```{r simul_no_compet_low_cor}
no_compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

```{r simul_no_compet_high_cor}
no_compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

```{r simul_compet_no_corr}
compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

```{r simul_compet_low_corr}
compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

```{r simul_compet_high_corr}
compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

no_compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width,
                 K = K)
    })

@@

```{r simul_no_compet_low_cor var_strength}
no_compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width,
                 K = K)
    })

@@

```{r simul_no_compet_high_cor var_strength}
no_compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, d = d,
                 k = k, width = var_width,
                 K = K)
    })

@@

```{r simul_compet_no_corr var_strength}
compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width,
                 K = K)
    })

@@

```{r simul_compet_low_corr var_strength}
compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width, K = K)
    })

@@

```{r simul_compet_high_corr var_strength}
compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width, K = K)
    })
